### 2014-01-31 analysis/Outline.rmd
Functional balance (fine root - leaf mass) in outline.rmd

@@

## Crown width and surface area

@@

with(dfr, plot(log_m.so, log_m.lf.fraction, axes=FALSE,
               xlab="Aboveground biomass (kg)",
               ylab="Leaf mass fraction (-)",
               pch=19, col=pft
))
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
box()
legend("topright", levels(dfr$pft), pch=19, col=palette())
```

>>>>

```{r echo=FALSE}
dfr <- subset(data, !is.na(m.rf) & !is.na(m.lf) & pft != "")
dfr$pft <- as.factor(dfr$pft)

palette(rich.colors(4))
with(dfr, plot(log10(m.lf), log10(m.rf),
               axes=FALSE,
               xlab="Leaf biomass (kg)",
               ylab="Fine root biomass (kg)",
               pch=19,
               col=pft))
zs <- c(0.05, 0.25, 0.5, 0.75,1)
for(z in zs)abline(log10(z),1)
legend("bottomright", levels(dfr$pft), pch=19, col=palette())
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
box()
```
Figure X. Lines are with exponent of 1, and represent fixed ratios between fine root biomass and leaf biomass (from top to bottom: 1, 0.75, 0.5, 0.25, 0.05).

@@

@@

with(dfr, plot(log_m.so, log_m.lf.fraction, axes=FALSE,
               xlab="Aboveground biomass (kg)",
               ylab="Leaf mass fraction (-)",
               pch=19, col=pft
))
magaxis(side=c(1,2), unlog='xy', tcl=-0.4)
box()
legend("topright", levels(dfr$pft), pch=19, col=palette())
```
Figure X. Much higher leaf mass fraction for evergreen gymnosperms at a given total aboveground plant biomass.
